Towards a miniKanren with fair search strategies

### 2019-05-23 Paper/paper.tex
Too many changes

\usepackage{listings}
\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh,disj,conj,disj+},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true,
  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
  		   {→}{{$\rightarrow$}}{1}
  		   {×}{{$\times$}}{1}
  		   {==}{{$\equiv$}}{1}
  		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
                   {appendo}{{append$^o$}}{6}
  		   {repeato}{{repeat$^o$}}{6}
  		   {g0}{{g$_0$}}{2}
  		   {g1}{{g$_1$}}{2}
  		   {g2}{{g$_2$}}{2}
  		   {gl}{{g$_l$}}{2}
  		   {gr}{{g$_r$}}{2}
  		   {DFSi }{{DFS$_\textrm{i}$}}{3}
  		   {DFSbi}{{DFS$_\textrm{bi}$}}{3}
  		   {DFSf }{{DFS$_\textrm{f}$}}{3}
}
%% scheme-list .

@@

\newcommand{\veryrecursiveo}{\texttt{very-recursive$^o$}}
\newcommand{\appendo}{\texttt{append$^o$}}
\newcommand{\reverso}{\texttt{revers$^o$}}
\newcommand{\repeato}{\texttt{repeat$^o$}}

\newcommand{\DFSi }[0]{DFS$_\textrm{i}$}
\newcommand{\DFSf }[0]{DFS$_\textrm{f}$}
\newcommand{\DFSbi}[0]{DFS$_\textrm{bi}$}
\newcommand{\BFS}[0]{BFS}
\newcommand{\BFSser}[0]{BFS$_\textrm{ser}$}
\newcommand{\BFSimp}[0]{BFS$_\textrm{imp}$}

@@

miniKanren is a family of relational programming languages.
\citep{Friedman:2005:RS:1121583} \citet{friedman_reasoned_2018} introduce 
miniKanren and its implementation in \emph{The Reasoned Schemer} 
and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). \citet{byrd2017unified} have 
demonstrated that miniKanren programs are useful in solving several problems.
miniKanren.org contains the seeds of many more problems and their solutions.

\NOTE[DPF]{... Perhaps it should be part of the title that we have improved on 
the the standard BFS implementation.}
\NOTE[DPF]{When you rewrite the abstract and drop the abbreviations, remember 
when you are rewriting the Introduction and introducing the abbreviations, that 
you should explain the ser of BFSser using a reference.}
\NOTE[LKC]{I have rewritten the abstract and explain the `ser' in the ending 
paragraph of introduction, where we list contributions.}

@@

To summarize our contributions, we
\begin{itemize}
	\item propose and implement \textbf{b}alanced \textbf{i}nterleaving 
depth-first search (\DFSbi{}), a new search strategy with almost-fair \disj{}.
	\item propose and implement \textbf{f}air depth-first search (\DFSf{}), 
a new search strategy with fair \disj{}.
	\item implement in a new way the standard breath-first search (\BFS), a 
search strategy with fair \disj{} and fair \conj{}. We name the current 
implementation by \citeauthor{seres1999algebra} as \BFSser{}, and our 
new implementation as \BFSimp{}. We prove formally that they are semantically 
equivalent. \BFSimp{}, however, runs faster in all benchmarks and is shorter, 
thus being an \textbf{imp}rovement. 
\end{itemize}

@@

\NOTE[DPF]{I think that should be said as directly as in your note.}
\NOTE[LKC]{I state this fact at the beginning of this section.

``We never use run* in this paper because fairness is only 
interesting when we have an unbounded number of answers. However, it is 
perfectly fine to use run* with any search strategies.''}

@@

\NOTE[DPF]{Next to the last line of the above paragraph the word same
has too many meanings.  It could be have the same cost or it could be
failing to distinguish two list that would be the same if we substituted
a b for an a.  It needs to be clarified.  It might help to work out
the actual numbers}
\NOTE[LKC]{I have rewritten the relevant sentences.}

@@

In this section, we review the implementation of interleaving depth-first 
search (\DFSi). We focus on parts that are relevant to this paper. TRS2,
chapter 10 and the appendix, ``Connecting the wires'', 
provides a comprehensive description of the 
miniKanren 
implementation but limited to unification constraints ($\equiv$).
Fig.~\ref{DFSi-0} and Fig.~\ref{DFSi-1} show parts that are later compared 
with other search 
strategies. We follow some conventions to name variables: \texttt{s}s name 
states; \texttt{g}s (possibly with subscript) name goals; 
variables ending with $^\infty$ name search spaces. Fig.~\ref{DFSi-0} shows the 
implementation of \disj. The 
first function, \texttt{disj2}, implements binary disjunction. It applies the 
two disjunctive goals to the input state \texttt{s} and composes the two 
resulting search spaces with \texttt{append$^\infty$}. The following syntax 
definitions say \disj{} is right-associative. Fig.~\ref{DFSi-1} 
shows the implementation of \conj. The first function, \texttt{conj2}, 
implements binary conjunction. 
It applies the \emph{first} goal to the input state, then applies the second 
goal to states in the resulting search space. The helper function 
\texttt{append-map$^\infty$} applies its input goal to states 
in its input search spaces and composes the resulting search spaces. It reuses 
\texttt{append$^\infty$} for search space composition. The following syntax 
definitions say \conj{} is also right-associative.
% \begin{figure}
% 	\lstinputlisting{Figures/conde.rkt}
% 	\caption{implementation of \conde}
% 	\label{conde}
% \end{figure}
% 
% The definition of \conde{} (Fig.~\ref{conde}) is shared by all search 
% strategies. It relates clauses disjunctively, and goals in the same 
% clause conjunctively.

\NOTE[DPF]{This came out fabulous. I think I spotted some missed opportunities
later, which I will point out with additional notes.}
\NOTE[LKC]{I think we can simply remove \conde{} code and its accompany 
description.}

@@

Balanced interleaving DFS (\DFSbi{}) has an almost-fair \disj{} and unfair 
\conj{}. The implementation of \DFSbi{} differs from 
\DFSi{}'s in the \disj{} macro. We list the new \disj{} with its 
helper in Fig.~\ref{balanced-disj}. When there are one or more disjunctive 
goals, \disj{} builds a balanced binary tree whose leaves are the goals and 
whose nodes are \texttt{disj2}s, hence the name of this search strategy. 
The new helper, \texttt{disj+}, takes two additional `arguments'. They 
accumulate goals to be put in the left and right subtrees. The first clause 
handles the case where there is only one goal. In this case, the tree is the 
goal itself. When there are more goals, we partition the list of goals 
into two sublists of roughly equal lengths and recur on the two sublists. We 
move goals to the accumulators in the last clause. As we are moving 
two goals each time, there are two base cases: (1) no goal remains; (2) one 
goal remains. We handle these two new base cases in the second clause and the 
third clause, respectively. In contrast, the \disj{} in \DFSi{} constructs the 
binary tree in a particularly unbalanced form.

@@

Fair DFS (\DFSf) has fair \disj{} and unfair \conj{}. The 
implementation of \DFSf{} differs from \DFSi{}'s in 
\texttt{disj2} (Fig.~\ref{fDFS}). The new \texttt{disj2} calls a new and 
fair version of \texttt{append$^\infty$}. \texttt{append$^\infty_{fair}$} 
immediately 
calls 
its helper, \texttt{loop}, with the first argument, \texttt{s?}, set to 
\texttt{\#{}t}, which indicates that we haven't swapped
\texttt{s$^\infty$} and \texttt{t$^\infty$}. The swapping 
happens at 
the third \texttt{cond} clause in the helper, where \texttt{s?} is updated 
accordingly. The first two \texttt{cond} clauses essentially copy the 
\texttt{car}s and stop recursion when one of the input spaces is obviously 
finite. The third clause, as we mentioned above, is just for swapping. When the 
fourth and last clause runs, we know that both \texttt{s$^\infty$} and 
\texttt{t$^\infty$} are ended with a thunk, and that we have swapped them. In 
this case, we construct a new thunk. The new thunk swaps two spaces back in the
recursive call to \texttt{loop}. This is unnecessary for fairness. We do it to 
produce answers in a more natural order.

@@

\NOTE[LKC]{Applying the above changes won't result in \BFSser, but yet 
another implementation of \BFS.}

@@

This implementation is improvable in two ways. 
First, as mentioned in \autoref{sec:fairconj}, \BFS{} puts answers in bags and 
answers of the same cost are in the same bag. In this implementation, however, 
we manage cost information subtly---the \texttt{car}s of a search space have 
cost 0 (i.e. they are all in the same bag), and every thunk indicates an 
increment in cost. It is even more subtle that \texttt{append$^\infty_{fair}$} 
and the \texttt{append-map$^\infty_{fair}$} respects the cost information. 
Second, \texttt{append$^\infty_{fair}$} is extravagant in memory usage. It 
makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
``length''s of input search spaces.

\NOTE[LKC]{Should I point out that \DFSf{} also has the miserable space 
extravagance?}

In the following subsections, we firstly describe \BFSimp{}, an improved \BFS{} 
implementation which manages cost information in a more clear way and is less 
extravagant in memory usage. Then we compare \BFSimp{} with \BFSser{}, the 
current implementation by \citeauthor{seres1999algebra}.

@@

\begin{figure}
	\lstinputlisting{Figures/BFSimp.rkt}	
	\caption{new and changed functions in optimized BFS that implements pure 
	features}
	\label{BFSimp}
\end{figure}

@@

\begin{figure}
	\lstinputlisting{Figures/BFSimp-cont.rkt}	
	\caption{new and changed functions in improved BFS that implement impure 
		features}
	\label{BFSimp-cont}
\end{figure}

@@

@@

In this subsection, we compare the pure subset of \BFSimp{} with \BFSser{}. We 
focus on the pure subset because \BFSser{} is designed for a pure 
relational programming system. We proof in Coq that these two search strategies 
are are semantically equivalent, (i.e., \texttt{(run n ? g)} produces the same 
result (See supplements for the formal proof). To compare efficiency, we 
translate \BFSser{}'s Haskell code into Racket (See supplements for the 
translated code). The translation is direct due to the similarity in two 
relational programming systems. The translated code is longer than \BFSimp{}. 
And it runs slower in all benchmarks. Details about differences in efficiency 
are in \autoref{compare-efficiency}.

@@

In this section, we compare the efficiency of search strategies. A concise 
description is in Table~\ref{compare-efficiency}. A hyphen means ``running out
of memory.'' The first two benchmarks are from 
TRS2. \reverso is from 
\citet{rozplokhas2018improving}. The next two benchmarks 
about quine are modified from a similar test case in \citet{byrd2017unified}. 
The modifications are made 
to circumvent the need for symbolic constraints (e.g. $\neq$, 
\texttt{absent$^o$}). Our version generates de 
Bruijnized expressions and prevents closures from being inside a list. The two 
benchmarks differ in the \conde{} clause order of their relational 
interpreters. 
The last two 
benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
you)}. This benchmark is from \citet{byrd2017unified}. Again, the 
sibling benchmarks differ in the \conde{} clause order of their relational 
interpreters. The first one 
has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
end, while the other has them at the beginning. We conjecture that \DFSi{} 
would 
perform badly in the second case because elimination rules complicate the 
problem when synthesizing (i.e., our evaluation supports our conjecture.)

In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{} is just 
as efficient in all benchmarks but \veryrecursiveo. Both implementations of BFS 
have obvious overhead in many cases. Among the three variants of DFS, which all 
all have unfair \conj{}), \DFSf{} is most resistant to clause permutation, 
followed by \DFSbi{} then \DFSi{}. Among the two implementation of BFS, our 
improved \BFSimp{} constantly performs as well or better. Interestingly, every 
strategy with fair \disj{} suffers in \veryrecursiveo{} and \DFSf{} performs 
well elsewhere. Therefore, this benchmark might be a special case. Fair \conj{} 
imposes considerable overhead constantly except in \appendo. The reason might be 
that strategies with fair \conj{} tend to keep more intermediate answers in the 
memory.

@@

@@

Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
alternatives to \DFSi{}, the current search strategy, 
and that \BFS{} is less practical.
% and that \BFSser{} is less practical than other breadth-first strategies.

Our new implementation of \BFS{} is semantically equivalent to the original 
one. But, ours is shorter and performs better in comparison with a 
straightforward translation of their Haskell code.

>>>>

\usepackage{listings}
\lstset{
  language=Scheme,
  basicstyle=\ttfamily,
  morekeywords={run,conde,run*,defrel,==,fresh,disj,conj,disj+},
  alsodigit={!\$\%&*+-./:<=>?@^_~},
  morecomment=[l]{;,\#{}lang},
  mathescape=true,
  literate={-inf}{{$^\infty$}}{1} {/fair}{{$_{fair}$}}{3}
  		   {→}{{$\rightarrow$}}{1}
  		   {×}{{$\times$}}{1}
  		   {==}{{$\equiv$}}{1}
  		   {conde}{{\textcolor[rgb]{0,.3,.7}{\textbf{cond$^e$}}}}{4}
                   {appendo}{{append$^o$}}{6}
  		   {repeato}{{repeat$^o$}}{6}
  		   {disj2}{{disj$_2$}}{4}
  		   {conj2}{{conj$_2$}}{4}
  		   {g0}{{g$_0$}}{2}
  		   {g1}{{g$_1$}}{2}
  		   {g2}{{g$_2$}}{2}
  		   {gl}{{g$_l$}}{2}
  		   {gr}{{g$_r$}}{2}
  		   {DFSi }{{DFS$_\textrm{i}$}}{3}
  		   {DFSbi}{{DFS$_\textrm{bi}$}}{3}
  		   {DFSf }{{DFS$_\textrm{f}$}}{3}
}
%% scheme-list .

@@

\newcommand{\disjtwo}{\texttt{disj$_2$}}
\newcommand{\conjtwo}{\texttt{conj$_2$}}
\newcommand{\veryrecursiveo}{\texttt{very-recursive$^o$}}
\newcommand{\appendo}{\texttt{append$^o$}}
\newcommand{\reverso}{\texttt{revers$^o$}}
\newcommand{\repeato}{\texttt{repeat$^o$}}

\newcommand{\DFSi }[0]{DFS$_\textrm{i}$}
\newcommand{\DFSf }[0]{DFS$_\textrm{f}$}
\newcommand{\DFSbi}[0]{DFS$_\textrm{bi}$}
\newcommand{\BFS}[0]{BFS}
\newcommand{\BFSser}[0]{BFS$_\textrm{}$}
\newcommand{\BFSimp}[0]{BFS$_\textrm{imp}$}

@@

miniKanren is a family of relational programming languages.
\citep{Friedman:2005:RS:1121583} \citet{friedman_reasoned_2018} introduce 
miniKanren and its implementation in \emph{The Reasoned Schemer} 
and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). \citet{byrd2017unified} have 
demonstrated that miniKanren programs are useful in solving several difficult
problems. miniKanren.org contains the seeds of many difficult problems and 
their solutions.

\NOTE[DPF]{[2,3] is the way to cite this, but I leave cleaning up this
paragraph to you.  Mostly the point is to also include a reference to
the two dimitris and to the first OCamren (OCanren), whatever. It is up to you
in this paragraph.  You can refer to
the two books like this ``Friedman et al[2,3] ... .'' This way the 
paragraph will have only one ``Friedman''}

\NOTE[DPF]{I have decided to agree with you that we should not use 
BFSser, so I am going to remove all occurrences.  
Also, we should say, ``Our implementation of BFS''
and then say, shortened to ``Our BFS'' and then you can use it in the table,
so one column should be Our BFS and the other should be BFS.}
\NOTE[DPF]{Occurrences of BFS (without Our) mean Seres et al. (We need only say
that once, or very occasionally}

\NOTE[DPF]{I think that subscripts i, bi, and f should
match what is in the comments above code, so it should be italic, emph,
or math, whichever was used before.}

\NOTE[DPF]{Is the spelling of reverso truly written without the last e?
Shouldn't it be reverseo with the appropriate raising of o.}

@@

To summarize our contributions, we
\begin{itemize}
	\item propose and implement \textbf{b}alanced \textbf{i}nterleaving 
depth-first search (\DFSbi{}), a new search strategy with almost-fair \disj{}.
	\item propose and implement \textbf{f}air depth-first search (\DFSf{}), 
a new search strategy with fair \disj{}.
	\item implement in a new way the standard breath-first search (\BFS), a 
search strategy with fair \disj{} and fair \conj{}. We name the current 
implementation by \citeauthor{seres1999algebra} and refer to ``our 
BFS implementation as the improved one. We formally prove
that the two BFS implementations are semantically 
equivalent, however, our BFS implementation runs faster in all 
benchmarks and is shorter.
\end{itemize}

@@

\NOTE[DPF]{Was this supposed to be a note?
``We never use \texttt{run*} in this paper because fairness is only 
 interesting when we have an unbounded number of answers. However, it is 
 perfectly fine to use run* with any search strategies.''}

@@

\NOTE[DPF]{Would the answer be the same if the list had been this ((a) (b))
or did you mean structurally the same?}
\NOTE[LKC]{I have rewritten the relevant sentences.}

@@

In this section, we review the implementation of interleaving depth-first 
search (\DFSi). We focus on parts that are relevant to this paper. TRS2,
chapter 10 and the appendix, ``Connecting the wires'', 
provides a comprehensive description of the 
miniKanren 
implementation but limited to unification constraints ($\equiv$).
Fig.~\ref{DFSi-0} and Fig.~\ref{DFSi-1} show parts that are later compared 
with other search 
strategies. We follow some conventions to name variables: \texttt{s}s name 
states; \texttt{g}s (possibly with subscript) name goals; 
variables ending with $^\infty$ name search spaces. Fig.~\ref{DFSi-0} shows the 
implementation of \disj. The 
first function, \disjtwo, implements binary disjunction. It applies the 
two disjunctive goals to the input state \texttt{s} and composes the two 
resulting search spaces with \texttt{append$^\infty$}. The following syntax 
definitions say \disj{} is right-associative. Fig.~\ref{DFSi-1} 
shows the implementation of \conj. The first function, \conjtwo{}, 
implements binary conjunction. 
It applies the \emph{first} goal to the input state, then applies the second 
goal to states in the resulting search space. The helper function 
\texttt{append-map$^\infty$} applies its input goal to states 
in its input search spaces and composes the resulting search spaces. It reuses 
\texttt{append$^\infty$} for search space composition. The following syntax 
definitions say \conj{} is also right-associative.
% \begin{figure}
% 	\lstinputlisting{Figures/conde.rkt}
% 	\caption{implementation of \conde}
% 	\label{conde}
% \end{figure}
% 
% The definition of \conde{} (Fig.~\ref{conde}) is shared by all search 
% strategies. It relates clauses disjunctively, and goals in the same 
% clause conjunctively.

\NOTE[DPF]{sure, go ahead and do it.}
\NOTE[LKC]{I think we can simply remove \conde{} code and its accompany 
description.}

@@

Balanced interleaving DFS (\DFSbi{}) has an almost-fair \disj{} and unfair 
\conj{}. The implementation of \DFSbi{} differs from 
\DFSi{}'s in the \disj{} macro. We list the new \disj{} with its 
helper in Fig.~\ref{balanced-disj}. When there are one or more disjunctive 
goals, \disj{} builds a balanced binary tree whose leaves are the goals and 
whose nodes are \disjtwo{}s, hence the name of this search strategy. 
The new helper, \texttt{disj+}, takes two additional `arguments'. They 
accumulate goals to be put in the left and right subtrees. The first clause 
handles the case where there is only one goal. In this case, the tree is the 
goal itself. When there are more goals, we partition the list of goals 
into two sublists of roughly equal lengths and recur on the two sublists. We 
move goals to the accumulators in the last clause. As we are moving 
two goals each time, there are two base cases: (1) no goal remains; (2) one 
goal remains. We handle these two new base cases in the second clause and the 
third clause, respectively. In contrast, the \disj{} in \DFSi{} constructs the 
binary tree in a particularly unbalanced form.

@@

Fair DFS (\DFSf) has fair \disj{} and unfair \conj{}. The 
implementation of \DFSf{} differs from \DFSi{}'s in 
\disjtwo{} (Fig.~\ref{fDFS}). The new \disjtwo{} calls a new and 
fair version of \texttt{append$^\infty$}. \texttt{append$^\infty_{fair}$} 
immediately 
calls 
its helper, \texttt{loop}, with the first argument, \texttt{s?}, set to 
\texttt{\#{}t}, which indicates that we haven't swapped
\texttt{s$^\infty$} and \texttt{t$^\infty$}. The swapping 
happens at 
the third \texttt{cond} clause in the helper, where \texttt{s?} is updated 
accordingly. The first two \texttt{cond} clauses essentially copy the 
\texttt{car}s and stop recursion when one of the input spaces is obviously 
finite. The third clause, as we mentioned above, is just for swapping. When the 
fourth and last clause runs, we know that both \texttt{s$^\infty$} and 
\texttt{t$^\infty$} are ended with a thunk, and that we have swapped them. In 
this case, we construct a new thunk. The new thunk swaps two spaces back in the
recursive call to \texttt{loop}. This is unnecessary for fairness. We do it to 
produce answers in a more natural order.

@@

\NOTE[DPF]{I need clarification: Applying the above changes won't result in ``our \BFS,'' but yet a third implementation of \BFS?}

@@

This implementation is improvable in two ways. 
First, as mentioned in \autoref{sec:fairconj}, \BFS{} puts answers in bags and 
answers of the same cost are in the same bag. In our implementation, however, 
we manage cost information subtly---the \texttt{car}s of a search space have 
cost 0 (i.e., they are all in the same bag), and every thunk indicates an 
increment in cost. It is even more subtle that \texttt{append$^\infty_{fair}$} 
and the \texttt{append-map$^\infty_{fair}$} respects the cost information. 
Second, \texttt{append$^\infty_{fair}$} is extravagant in memory usage. It 
makes $O(n+m)$ new \texttt{cons} cells every time, where $n$ and $m$ are the 
``length''s of input spaces.

\NOTE[LKC]{Should I point out that \DFSf{} also has the miserable space 
extravagance?}
\NOTE[DPF]{probably}

In the following subsections, we first describe our improved \BFS{}
implementation that manages cost information in a more clear and concise
way and is less extravagant in memory usage. 
Then we compare our BFS{} with \BFS{}, the 
current implementation by \citeauthor{seres1999algebra}.

\NOTE[DPF]{Let's use one more line and far less horizontal space
by use 3 linefeeds.  They will still align nicely.}

@@

\begin{figure}
	\lstinputlisting{Figures/BFSimp.rkt}	
	\caption{New and changed functions in optimized BFS that implements pure 
	features}
	\label{BFSimp}
\end{figure}

@@

\NOTE[DPF]{I am not in love with the two calls to null?. I can think of at least
two ways to fix it.  Pick one.}

\begin{figure}
	\lstinputlisting{Figures/BFSimp-cont.rkt}	
	\caption{New and changed functions in improved BFS that implement impure 
		features}
	\label{BFSimp-cont}
\end{figure}

\NOTE[DPF]{The use of the references to Fig 7 twice tells me that something
has to change for the sake of clarity.}

@@

\NOTE[DPF]{If we forget to use {} after \reverso, the o ends up too near
the next word.  I fixed reverso on the second line of section 7, but there 
may be others.}

@@

In this subsection, we compare the pure subset of our BFS with \BFS{}. We 
focus on the pure subset because \BFS{} is designed for a pure 
relational programming system. We prove in Coq that these two search strategies 
are are semantically equivalent, since \texttt{(run n ? g)} produces the same 
result in both our improved \BFS{} and BFS. (See supplements for the formal proof.) To compare efficiency, we 
translate \BFS{}'s Haskell code into Racket (See supplements for the 
translated code). The translation is direct due to the similarity of the two 
relational programming systems. The translated code is longer than our \BFS{}. 
And it runs slower in all benchmarks. Details about differences in efficiency 
are in \autoref{compare-efficiency}.

@@

In this section, we compare the efficiency of search strategies. A concise 
description is in Table~\ref{compare-efficiency}. A hyphen means ``running out
of memory.'' The first two benchmarks are from 
TRS2. \reverso{} is from 
\citet{rozplokhas2018improving}. The next two benchmarks 
about quine are modified from a similar test case in \citet{byrd2017unified}. 
The modifications are made 
to circumvent the need for symbolic constraints (e.g. $\neq$, 
\texttt{absent$^o$}). Our version generates de 
Bruijnized expressions and prevents closures from being inside a list. The two 
benchmarks differ in the \conde{} clause order of their relational 
interpreters. 
The last two 
benchmarks are about synthesizing expressions that evaluate to \texttt{'(I love 
you)}. This benchmark is from \citet{byrd2017unified}. Again, the 
sibling benchmarks differ in the \conde{} clause order of their relational 
interpreters. The first one 
has elimination rules (i.e. application, \texttt{car}, and \texttt{cdr}) at the 
end, while the other has them at the beginning. We conjecture that \DFSi{} 
would 
perform badly in the second case because elimination rules complicate the 
problem when synthesizing (i.e., our evaluation supports our conjecture.)

\NOTE[DPF]{There is still some clumsiness using our improved DFS, since
at some point, we may want to make this clearer, so have DFS not be fonted
is a little weird.  I think both should always use ourDFS and 
macro expand it to <our improved DFS>.  Then changes will be much easier.}

In general, only \DFSi{} and \DFSbi{} constantly perform well. \DFSf{}
is just as efficient in all benchmarks except those of \veryrecursiveo. Both
implementations of BFS have obvious overhead in many cases. Among the
three variants of DFS, which all have unfair \conj{}, \DFSf{} is most
resistant to clause permutation, followed by \DFSbi{} then
\DFSi{}. Among the two implementation of BFS, our improved \BFS{}
constantly performs as well or better. Interestingly, every strategy
with fair \disj{} suffers in \veryrecursiveo{} and \DFSf{} performs
well elsewhere. Therefore, this benchmark might be a special
case. Fair \conj{} imposes considerable overhead constantly except in
\appendo. The reason might be that strategies with fair \conj{} tend
to keep more intermediate answers in the memory.

@@

\NOTE[DPF]{We might find the reference Ocanren in the two Dmitri's paper
and say something here about it.}

@@

Our quantitative evaluation shows that \DFSbi{} and \DFSf{} are competitive 
alternatives to \DFSi{}, the current search strategy miniKanren
and that \BFS{} is less practical.
% and that \BFSser{} is less practical than other breadth-first strategies.

Our improved \BFS{} is semantically equivalent to the original 
one. But, ours is shorter and performs better in comparison with a 
straightforward translation of their Haskell code.
